%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Artificial Intelligence Student} % Job title
    {University of Pisa} % Organization
    {Pisa, Italy} % Location
    {Mar. 2019 - Present} % Date(s)
    {   
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In the context of \textbf{Artificial Intelligence Fundamentals} exam, in the fields of \textit{Search, Constraint Satisfaction Problem (CSP), Logic} and \textit{Planning}, I developed several algorithms for solving problems formulated according to one of these models, such as \textit{AC3b}, \textit{AC4}, \textit{GAC}, \textit{CDCL}, etc., paying particular attention to the definition, where possible, of translators able to convert a specific problem's definition as one of these model, according to another model, allowing their resolution trough the typical algorithms of this field. Some examples are \textit{SearchPlan}, \textit{CSPlan}, \textit{SATPlan}, etc.. All of these algorithms was submitted and merged in the Python GitHub repository of Norvig's book, \textit{Artificial Intelligence, A Modern Approach}.}
        \item {In the context of \textbf{Machine Learning} and \textbf{Numerical Methods and Optimization} exam, I developed several machine learning and numerical optimization algorithms used by the latter and which was both submitted and merged in the Python GitHub repository of Norvig's book, \textit{Artificial Intelligence, A Modern Approach}. All of these can be found also in my GitHub repository and represents a highly modular project as well as a reference point for students of the following years.}
      \end{cvitems}
    }
    
  \cventry
    {Data Scientist} % Job title
    {Exprivia S.p.A.} % Organization
    {Molfetta, Bari, Italy} % Location
    {Sept. 2018 - Feb. 2019} % Date(s)
    {   
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In the context of \textbf{Industry 4.0} for the \textit{Predictive Maintenance} scenario, I deployed as a Docker container an end-to-end Machine Learning platform for Multiple Multivariate Time Series Prediction from extraction of simple statistical features (eg. means, standard deviations, maximum and minimum values, skewness, kurtosis, etc.) and typical domain type related features (eg. Fourier transform, etc.) to model-building to predictions. 
This platform has two main components: a web frontend written in JavaScript that allows interactive exploration of machine learning pipeline and a backend written in Python and composed by Cesium ML algorithms for time-series inference (eg. Random Forest, Linerar Regression, etc.) and a Long Short Term Memory (LSTM) Recurrent Neural Network (RNN) model trained in Keras.}
        \item {In the context of \textbf{Smart City} for the \textit{Smart Bins} scenario, I trained a Convolutional Neural Network (CNN) for the recognition of waste to be differentiated into paper, plastic, glass or undifferentiated and I deployed as a Docker container in Tensorflow Serving to made it available through RESTful API.}
        \item {In view of the participation at the \textbf{Mobile World Congress 2019} in Barcelona I deployed in TensorFlow Serving a pre-trained object detection model for the real-time recognition and counting of people present on all Exprivia S.p.A. stands.}
      \end{cvitems}
    }

%---------------------------------------------------------



%---------------------------------------------------------
\end{cventries}
