%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Optimizers for/and sklearn compatible Machine Learning models.} % Description
    {OptiML} % Name
    {Python} % Tools Used
    {\href{https://github.com/dmeoli/optiml}{github.com/dmeoli/optiml}} % Link
    {}
    
%---------------------------------------------------------
  \cventry
    {Data Analysis of an Online Retail.} % Description
    {Online Retail} % Name
    {Python} % Tools Used
    {\href{https://github.com/dmeoli/OnlineRetail}{github.com/dmeoli/OnlineRetail}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {Prolog Expert System on Anxiety Disorders.} % Description
    {P.E.S.A.D.} % Name
    {Prolog} % Tools Used
    {\href{https://github.com/dmeoli/PESAD}{github.com/dmeoli/PESAD}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {Rule-based expert system, available as Telegram bot, which suggests a beer to drink according to taste and meal.} % Description
    {BeerEX} % Name
    {CLIPS, Python} % Tools Used
    {\href{https://github.com/dmeoli/BeerEX}{github.com/dmeoli/BeerEX}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {Social Media Analysis for the Discovery of Interaction Patterns.} % Description
    {BSc Thesis} % Name
    {Java} % Tools Used
    {\href{https://github.com/dmeoli/SocialMediaDiscovery}{github.com/dmeoli/SocialMediaDiscovery}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {Recognition System for online handwritten Signature verification based on a descriptive statistical approach.} % Description
    {DS-SRS} % Name
    {Matlab} % Tools Used
    {\href{https://github.com/dmeoli/DS-SRS}{github.com/dmeoli/DS-SRS}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {Search Engine for the Cranfield collection.} % Description
    {CranSearchEngine} % Name
    {Java} % Tools Used
    {\href{https://github.com/dmeoli/CranSearchEngine}{github.com/dmeoli/CranSearchEngine}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {A* heuristic Graph Search algorithm.} % Description
    {A* Search} % Name
    {C++} % Tools Used
    {\href{https://github.com/dmeoli/AStarSearch}{github.com/dmeoli/AStarSearch}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {WordNet Similarity for Java provides an API for several Semantic Relatedness/Similarity algorithms.} % Description
    {WS4J} % Name
    {Java} % Tools Used
    {\href{https://github.com/dmeoli/WS4J}{github.com/dmeoli/WS4J}} % Link
    {}

%---------------------------------------------------------
  \cventry
    {WordNet Affect allows to find the Emotion of a given word.} % Description
    {WNAffect} % Name
    {Java} % Tools Used
    {\href{https://github.com/dmeoli/WNAffect}{github.com/dmeoli/WNAffect}} % Link
    {}

%---------------------------------------------------------
\end{cventries}
